MSHS COVID-19 Vaccinations

### 2021-04-05 Evening-Huddle-Stats.Rmd
Update logic for this week's doses to date to include all dates, even holidays when there may not have been any appts scheduled or arrived.

@@

# Summarize data for this week to date -------------------
this_week_daily_admin <- daily_sched_summary %>%
  filter(VaccWeek == this_week &
           ApptDate < today) %>%
  group_by(Site, Dose, VaccWeek, ApptDate) %>%
  summarize(AdminDoses = sum(Count, na.rm = TRUE),
            .groups = "keep") %>%
  ungroup() %>%
  pivot_wider(names_from = c(VaccWeek, ApptDate),
              names_prefix = "Wk ",
              names_sep = c(": "),
              values_from = AdminDoses,
              names_sort = TRUE)

@@

  # Determine dates this week through yesterday
  this_weeks_dates <- format(
  sort(unique(daily_sched_summary %>%
                filter(VaccWeek == this_week &
                         ApptDate < today) %>%
                select(ApptDate))$ApptDate), "%m/%d/%y")

>>>>

# Create a template of this week's days for each site and dose to ensure holidays are included
this_week_prior_days <- all_dates %>%
  filter(VaccWeek == this_week &
           Date < today)

colnames(this_week_prior_days) <- c("ApptDate", "VaccWeek")

this_week_prior_days_rep <- bind_rows(replicate(length(all_sites),
                                              this_week_prior_days,
                                              simplify = FALSE))

site_this_week_prior_days_rep <- data.frame("Site" = sort(
  rep(all_sites, nrow(this_week_prior_days))))

site_this_week_prior_days_templ <- cbind(site_this_week_prior_days_rep,
                                     this_week_prior_days_rep)

site_dose_this_week_prior_days_templ <- left_join(site_dose_rep,
                                                site_this_week_prior_days_templ,
                                                by = c("Site" = "Site"))

@@

# Summarize data for this week to date -------------------
this_week_daily_admin <- daily_sched_summary %>%
  filter(VaccWeek == this_week &
           ApptDate < today) %>%
  group_by(Site, Dose, ApptDate) %>%
  summarize(AdminDoses = sum(Count, na.rm = TRUE),
            .groups = "keep") %>%
  ungroup()

# Combine with template to ensure holidays are included
this_week_daily_admin <- left_join(site_dose_this_week_prior_days_templ,
                                   this_week_daily_admin,
                                   by = c("Site" = "Site",
                                          "Dose" = "Dose",
                                          "ApptDate" = "ApptDate"))

# Pivot wider to get desired format
this_week_daily_admin <- this_week_daily_admin %>%
  pivot_wider(names_from = c(VaccWeek, ApptDate),
              names_prefix = "Wk ",
              names_sep = c(": "),
              values_from = AdminDoses,
              names_sort = TRUE)

@@

  # Determine dates this week through yesterday
  # this_weeks_dates <- format(
  # sort(unique(daily_sched_summary %>%
  #               filter(VaccWeek == this_week &
  #                        ApptDate < today) %>%
  #               select(ApptDate))$ApptDate), "%m/%d/%y")

  this_weeks_dates <- format(
    sort(this_week_prior_days %>%
           select(ApptDate))$ApptDate, "%m/%d/%y")
